Generalized Universe Hierarchies and First-Class Universe Levels

### 2021-06-05 arxivsub/preprint.tex
fix

\begin{mylemma} Every family morphism has invertible action on terms, i.e.\ there
is an $F^{-1} : \Tm\,\Gamma\,(F\,A) \to \Tm\,\Gamma\,A$.
\end{mylemma}
\begin{proof} From the
preservation of context extension by $F$, we know that $F$ is invertible on the zero De Bruijn
index, so for $\q : \Tm\,(\Gamma \ext F\,A)\,(F (A[\p]))$, we have $F^{-1}\q : \Tm\,(\Gamma \ext
F\,A)\,(A[\p])$, such that $F (F^{-1}\,\q) = \q$. If we have any $t : \Tm\,\Gamma\,(F\,A)$, we also
have $(F^{-1}\q)[\id,\,t] : \Tm\,\Gamma\,A$, and this yields the inverse action $F^{-1}$ which acts
on all terms.
\end{proof}

>>>>

\begin{mylemma} Every family morphism has invertible action on terms, i.e.\ there
  is an $F^{-1} : \Tm\,\Gamma\,(F\,A) \to \Tm\,\Gamma\,A$.
\end{mylemma}

\begin{proof}
From the $\ext$-preservation isomorphism and the defining isomorphisms of
comprehension, we get $\q' : \Tm\,(\Gamma \ext F\,A)\,(A[\p])$ such that $F\,\q'
= \q$ and $\q'[\p,\,F\,\q] = \q$. Now, for $t : \Tm\,\Gamma\,(F\,A)$, we
define $F^{-1}\,t$ as $\q'[\id,\,t] : \Tm\,\Gamma\,A$. We get the following:
\begin{alignat*}{3}
  & F(F^{-1}\,t) = F(\q'[\id,\,t]) = (F\,\q')[\id,\,t] = \q'[\id,\,t] = t \\
  & F^{-1}(F\,t) = \q'[\id,\,F\,t] = \q'[\id,\,(F\,\q)[\id,\,\,t]] = \q'[\p,\,F\,\q][\id,\,t]
    = \q[\id,\,t] = t
\end{alignat*}
More concisely, $F$ is invertible on the generic term $\q$, which implies invertibility
on any term.
\end{proof}
